Untitled

### 2022-06-10 Manuscript/Lanuza_et_al_2021.Rmd
edit

We selected a total of 19 different functional traits that comprised both reproductive and life history traits (see Table 1). From these, 16 were reproductive traits that consisted of 13 floral traits and 3 reproductive biology traits. Floral traits included morphological traits (e.g., style length) but also floral reward (e.g., pollen quantity) and floral display (e.g., number of flowers) related traits. Reproductive biology traits indicated the reproductive system of the plant and included breeding, mating and compatibility system. The 3 remaining traits were life history traits that are commonly used to characterize the fast-slow continuum of plant trait variation (i.e., plant height, lifespan and life form). For each plant species, we undertook an extensive literature and online search for all traits across a wide range of resources (plant databases, online floras, books, journals and images). From a total of 30,120 possible cells considering all traits and plant species (20 columns × 1,506 species), we were able to fill 24,341 cells (80.8% of the dataset, see Fig. S2 for missing values information for each trait). An extended description of each trait and how it was obtained can be found in Appendix S1.

@@

This study investigates the reproductive spectrum of flowering plants and shows that plants have clear positive and negative correlations between reproductive traits that determine interactions with floral visitors at a global scale. Despite the enormous variability of plant reproductive structures, three axes were able to capture over 70% of reproductive trait variation. The first axis was the flower number - flower size and described the negative association between flower number and flower size. Although this negative correlation has received substantial attention [worley2000; @sargent2007; @kettle2011], it has only been investigated across a few hundred of Angiosperm species and without a multitrait perspective. Here, we provide support to this evidence and show that also key reproductive traits to plant reproduction like ovule number and style length are positively correlated with flower size and negatively correlated with flower number. The second axis organized the species by the degree of pollinator dependence where species with higher pollinator dependence showed greater floral display.

@@

We found that there are three reproductive axes that capture over 70% of the reproductive trait variation: (i) the flower number - flower size axis, (ii) the pollinator dependence axis and (iii) the style length - pollinator dependence axis. These reproductive axes helped partly explain the presence of floral visitor interactions, but not their number of visits. However, floral visitor guilds formed distinct relationships with the main axes of trait variation. Finally, we found that the plant species network roles were best explained by plant size and floral reward related traits.

@@

To conclude, we provide a robust description of plant reproductive trade-offs using a large global dataset of plant traits. We identified the major reproductive strategies of flowering plants and how these strategies influence interactions with different floral visitor guilds. Although the explained variation that we found in the first two axes is lower than previous studies of vegetative traits [@diaz2016; @carmona2021] it is consistent with the largest and most recent study that has characterised plant life strategies with vegetative and reproductive traits [@salguero2016]. Future work needs to integrate the reproductive compromises that we have identified with vegetative and physiological trade-offs to create a more comprehensive spectrum of plant trait variation. Further, the varying level of phylogenetic signal among traits deserves further attention to understand evolutionary changes on mating and flower morphology in response to pollinators [@gervasi2017; @mackin2021]. Finally, including plant-pollinator networks from unrepresented areas of the world and a more complete description of plant reproductive trade-offs is essential for a better understanding of the global patterns in plant-pollinator interactions.

@@

  plot <- plot + xlab(paste("Flower number - flower size axis ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
  plot <- plot + ylab(paste("Pollinator dependence axis ", "(",(percentage[2]),"%",")", sep = "")) #YLAB

>>>>

We selected a total of 19 different functional traits that comprised reproductive traits and plant form and size related traits (see Table 1). From these, 16 were reproductive traits that consisted of 13 floral traits and 3 reproductive biology traits. Floral traits included traits related to the size of floral organs (e.g., style length), floral display (e.g., number of flowers) and floral rewards (e.g., pollen quantity). Reproductive biology traits indicated the reproductive system of the plant and included breeding, mating and compatibility system. The 3 remaining traits were plant size and form related traits that are commonly used to characterize the fast-slow continuum of plant trait variation (i.e., plant height, lifespan and life form). For each plant species, we undertook an extensive literature and online search for all traits across a wide range of resources (plant databases, online floras, books, journals and images). From a total of 30,120 possible cells considering all traits and plant species (20 columns × 1,506 species), we were able to fill 24,341 cells (80.8% of the dataset, see Fig. S2 for missing values information for each trait). An extended description of each trait and how it was obtained can be found in Appendix S1.

@@

This study investigates the reproductive spectrum of flowering plants and shows that plants have clear positive and negative correlations between reproductive traits that determine interactions with floral visitors at a global scale. Despite the enormous variability of plant reproductive structures, the first two and three axes were able to capture over 50% and 70% of reproductive trait variation, respectively. These three axes were: (1) the flower number - flower size, (2) the pollinator dependence - floral display and (3) the style length - pollinator dependence. Although the explained trait variation that we found in the first two axes is lower than previous studies that consider morphological and physiological traits [@diaz2016; @carmona2021], it is consistent with the largest and most recent study that has characterised plant life strategies with reproductive and plant form and size related traits [@salguero2016]. Interestingly, these different plant reproductive axes were able to partly explain the number of interacting partners of floral visitor guilds but insufficient to capture their visitation rates. This highlights the need to account for other factors such as species abundances [@ref] or biological mistmatches [@ref] to better capture the intensity of species interactions at a macroecological scale.

The first axis described the negative association between flower number and flower size. Although this negative correlation has received substantial attention [worley2000; @sargent2007; @kettle2011], it has only been investigated across a few hundred of Angiosperm species and without a multitrait perspective. Here, we provide support to this evidence and show that also key reproductive traits to plant reproduction like ovule number and style length are positively correlated with flower size and negatively correlated with flower number. The second axis organized the different species by the degree of pollinator dependence where species with higher pollinator dependence showed greater floral display.

@@

@@

To conclude, we provide a robust description of plant reproductive trade-offs using a large global dataset of plant traits. We identified the major reproductive strategies of flowering plants and how these strategies influence interactions with different floral visitor guilds. Future work needs to integrate the reproductive compromises that we have identified with vegetative and physiological trade-offs to create a more comprehensive spectrum of plant trait variation. Further, the varying level of phylogenetic signal among traits deserves further attention to understand evolutionary changes on mating and flower morphology in response to pollinators [@gervasi2017; @mackin2021]. Finally, including plant-pollinator networks from unrepresented areas of the world and a more complete description of plant reproductive trade-offs is essential for a better understanding of the global patterns in plant-pollinator interactions.

[Lo guardo aqui por si hay que rescatarlo](Jose)

[We found that there are three reproductive axes that capture over 70% of the reproductive trait variation: (i) the flower number - flower size axis, (ii) the pollinator dependence axis and (iii) the style length - pollinator dependence axis. These reproductive axes helped partly explain the presence of floral visitor interactions, but not their number of visits. However, floral visitor guilds formed distinct relationships with the main axes of trait variation. Finally, we found that the plant species network roles were best explained by plant size and floral reward related traits.](old text)

@@

  plot <- plot + xlab(paste("Flower number - flower size axis ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
  plot <- plot + ylab(paste("Pollinator dependence - floral display axis ", "(",(percentage[2]),"%",")", sep = "")) #YLAB

### 2022-06-10 Manuscript/Lanuza_et_al_2021.tex
edit

We selected a total of 19 different functional traits that comprised both reproductive and life history traits (see Table 1). From these, 16 were reproductive traits that consisted of 13 floral traits and 3 reproductive biology traits. Floral traits included morphological traits (e.g., style length) but also floral reward (e.g., pollen quantity) and floral display (e.g., number of flowers) related traits. Reproductive biology traits indicated the reproductive system of the plant and included breeding, mating and compatibility system. The 3 remaining traits were life history traits that are commonly used to characterize the fast-slow continuum of plant trait variation (i.e., plant height, lifespan and life form). For each plant species, we undertook an extensive literature and online search for all traits across a wide range of resources (plant databases, online floras, books, journals and images). From a total of 30,120 possible cells considering all traits and plant species (20 columns × 1,506 species), we were able to fill 24,341 cells (80.8\% of the dataset, see Fig. S2 for missing values information for each trait). An extended description of each trait and how it was obtained can be found in Appendix S1.

@@

This study investigates the reproductive spectrum of flowering plants and shows that plants have clear positive and negative correlations between reproductive traits that determine interactions with floral visitors at a global scale. Despite the enormous variability of plant reproductive structures, three axes were able to capture over 70\% of reproductive trait variation. One of the major covariation patterns of the reproductive trait space was the negative correlation between flower number and flower size that is a widely described association across (\protect\hyperlink{ref-kettle2011}{Kettle et al., 2011}; \protect\hyperlink{ref-sargent2007}{Sargent et al., 2007}) and within (\protect\hyperlink{ref-delph2004}{Delph et al., 2004}) Angiosperms species. Our study explore this association beyond a two-trait correlation and shows that other fundamental traits to plant reproduction are also negatively correlated to flower number like ovule number and style length.

@@

We found that there are three reproductive axes that capture over 70\% of the reproductive trait variation: (i) the flower number - flower size axis, (ii) the pollinator dependence axis and (iii) the style length - pollinator dependence axis. These reproductive axes helped partly explain the presence of floral visitor interactions, but not their number of visits. However, floral visitor guilds formed distinct relationships with the main axes of trait variation. Finally, we found that the plant species network roles were best explained by plant size and floral reward related traits.

@@

To conclude, we provide a robust description of plant reproductive trade-offs using a large global dataset of plant traits. We identified the major reproductive strategies of flowering plants and how these strategies influence interactions with different floral visitor guilds. Although the explained variation that we found in the first two axes is lower than previous studies of vegetative traits (\protect\hyperlink{ref-carmona2021}{Carmona et al., 2021}; \protect\hyperlink{ref-diaz2016}{Díaz et al., 2016}) it is consistent with the largest and most recent study that has characterised plant life strategies with vegetative and reproductive traits (\protect\hyperlink{ref-salguero2016}{Salguero-Gómez et al., 2016}). Future work needs to integrate the reproductive compromises that we have identified with vegetative and physiological trade-offs to create a more comprehensive spectrum of plant trait variation. Further, the varying level of phylogenetic signal among traits deserves further attention to understand evolutionary changes on mating and flower morphology in response to pollinators (\protect\hyperlink{ref-gervasi2017}{Gervasi \& Schiestl, 2017}; \protect\hyperlink{ref-mackin2021}{Mackin et al., 2021}). Finally, including plant-pollinator networks from unrepresented areas of the world and a more complete description of plant reproductive trade-offs is essential for a better understanding of the global patterns in plant-pollinator interactions.

>>>>

We selected a total of 19 different functional traits that comprised reproductive traits and plant form and size related traits (see Table 1). From these, 16 were reproductive traits that consisted of 13 floral traits and 3 reproductive biology traits. Floral traits included traits related to the size of floral organs (e.g., style length), floral display (e.g., number of flowers) and floral rewards (e.g., pollen quantity). Reproductive biology traits indicated the reproductive system of the plant and included breeding, mating and compatibility system. The 3 remaining traits were plant size and form related traits that are commonly used to characterize the fast-slow continuum of plant trait variation (i.e., plant height, lifespan and life form). For each plant species, we undertook an extensive literature and online search for all traits across a wide range of resources (plant databases, online floras, books, journals and images). From a total of 30,120 possible cells considering all traits and plant species (20 columns × 1,506 species), we were able to fill 24,341 cells (80.8\% of the dataset, see Fig. S2 for missing values information for each trait). An extended description of each trait and how it was obtained can be found in Appendix S1.

@@

This study investigates the reproductive spectrum of flowering plants and shows that plants have clear positive and negative correlations between reproductive traits that determine interactions with floral visitors at a global scale. Despite the enormous variability of plant reproductive structures, the first two and three axes were able to capture over 50\% and 70\% of reproductive trait variation, respectively. These three axes were: (1) the flower number - flower size, (2) the pollinator dependence - floral display and (3) the style length - pollinator dependence. Although the explained trait variation that we found in the first two axes is lower than previous studies that consider morphological and physiological traits (\protect\hyperlink{ref-carmona2021}{Carmona et al., 2021}; \protect\hyperlink{ref-diaz2016}{Díaz et al., 2016}), it is consistent with the largest and most recent study that has characterised plant life strategies with reproductive and plant form and size related traits (\protect\hyperlink{ref-salguero2016}{Salguero-Gómez et al., 2016}). Interestingly, these different plant reproductive axes were able to partly explain the number of interacting partners of floral visitor guilds but insufficient to capture their visitation rates. This highlights the need to account for other factors (e.g., species abundances or biological mistmatch) to better capture the intensity of species interactions at a macroecological scale.

The first axis described the negative association between flower number and flower size. Although this negative correlation has received substantial attention {[}worley2000; \protect\hyperlink{ref-sargent2007}{Sargent et al.} (\protect\hyperlink{ref-sargent2007}{2007}); \protect\hyperlink{ref-kettle2011}{Kettle et al.} (\protect\hyperlink{ref-kettle2011}{2011}){]}, it has only been investigated across a few hundred of Angiosperm species and without a multitrait perspective. Here, we provide support to this evidence and show that also key reproductive traits to plant reproduction like ovule number and style length are positively correlated with flower size and negatively correlated with flower number. The second axis organized the different species by the degree of pollinator dependence where species with higher pollinator dependence showed greater floral display.

As expected\ldots{} quizas hilar aqui con un par de refs para que quede menos results

it has been investigated empirically only just with few hundreds of Angiosperm species and without a multitrait perspective. The second axis of reproductive trait variation was the pollinator dependence axis and showed the variation

main covariation pattern of the reproductive trait space was the negative correlation between flower number and flower size that is a widely described association across (\protect\hyperlink{ref-kettle2011}{Kettle et al., 2011}; \protect\hyperlink{ref-sargent2007}{Sargent et al., 2007}) and within (\protect\hyperlink{ref-delph2004}{Delph et al., 2004}) Angiosperms species. Our study explore this association beyond a two-trait correlation and shows that other fundamental traits to plant reproduction are also negatively correlated to flower number like ovule number and style length.

@@

@@

To conclude, we provide a robust description of plant reproductive trade-offs using a large global dataset of plant traits. We identified the major reproductive strategies of flowering plants and how these strategies influence interactions with different floral visitor guilds. Future work needs to integrate the reproductive compromises that we have identified with vegetative and physiological trade-offs to create a more comprehensive spectrum of plant trait variation. Further, the varying level of phylogenetic signal among traits deserves further attention to understand evolutionary changes on mating and flower morphology in response to pollinators (\protect\hyperlink{ref-gervasi2017}{Gervasi \& Schiestl, 2017}; \protect\hyperlink{ref-mackin2021}{Mackin et al., 2021}). Finally, including plant-pollinator networks from unrepresented areas of the world and a more complete description of plant reproductive trade-offs is essential for a better understanding of the global patterns in plant-pollinator interactions.

\href{Jose}{Lo guardo aqui por si hay que rescatarlo}

\href{old\%20text}{We found that there are three reproductive axes that capture over 70\% of the reproductive trait variation: (i) the flower number - flower size axis, (ii) the pollinator dependence axis and (iii) the style length - pollinator dependence axis. These reproductive axes helped partly explain the presence of floral visitor interactions, but not their number of visits. However, floral visitor guilds formed distinct relationships with the main axes of trait variation. Finally, we found that the plant species network roles were best explained by plant size and floral reward related traits.}

### 2022-06-10 Supplementary_Material/Sup_Mat_Lanuza_et_al_2021_Ecology_Letters.Rmd
edit

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
 plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.7,5.05,5.6,7.85,7.3,6.15)), y = -(PCAloadings$PC2*c(4.693,2.5,3.1,6.6,5,5.5)+c(0,0,0,0,0.4,0)),
                         label = PCAloadings$Variables, color="black",fontface =2,size=4)

>>>>

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
 plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.7,5.05,5.6,7.85,7.3,6.15)), y = -(PCAloadings$PC2*c(4.693,2.5,3.1,6.6,5,5.5)+c(0,0,0,0,0.4,0)),
                         label = PCAloadings$Variables, color="black",fontface =2,size=4.5)
